Evolution of pre-copulatory and post-copulatory inbreeding behaviour

### 2016-09-29 ms_pre_post.Rmd
Add caveat that invasion of strategy results change for post-copulatory inbreeding avoidance when polyandry is fixed

---
title: "Evolution of pre-copulatory and post-copulatory inbreeding behaviour"
author: "A. Bradley Duthie et al."
date: "August 24, 2016"
output:
  pdf_document:
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
header-includes:
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 1
csl: evolution.csl
bibliography: ms_pre_post.bib
---

@@

When pre-copulatory inbreeding strategy was initialised for random mating, but polyandry and post-copulatory inbreeding strategy allele values were fixed for adaptive inbreeding avoidance (Figure 4A,B), negative pre-copulatory inbreeding allele values became increasingly more frequent ($M_{a}<0$), causing inbreeding avoidance in mate choice. However, $M_{a}$ values were not as negative after $40000$ generations when post-copulatory inbreeding avoidance and polyandry were fixed as they were when no post-copulatory inbreeding avoidance occurred (e.g., compare Figure 4A with Figure 1A, and Figure 4B with Figure 2A). When post-copulatory inbreeding strategy was initialised for random fertilisation, existence of an already adaptive strategy of pre-copulatory inbreeding avoidance precluded evolution of polyandry and post-copulatory inbreeding avoidance (Figure 4C,D). Mean allele values affecting polyandry consistently decreased over generations regardless of the cost of post-copulatory inbreeding strategy, $c_{F}$. Consequently, when $c_{F}=0$, post-copulatory inbreeding strategy allele values had no effect because females were consistently monandrous, resulting in high drift of $F_{a}$ values among replicates (Figure 4C). However, when $c_{F}=0.02$, $F_{a}$ values remained near zero to minimise direct costs.

>>>>

---
title: "Evolution of pre-copulatory and post-copulatory inbreeding behaviour"
author: "A. Bradley Duthie et al."
date: "August 24, 2016"
output:
  pdf_document:
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
header-includes:
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 2
csl: evolution.csl
bibliography: ms_pre_post.bib
---

@@

When pre-copulatory inbreeding strategy was initialised for random mating, but polyandry and post-copulatory inbreeding strategy allele values were fixed for adaptive inbreeding avoidance (Figure 4A,B), negative pre-copulatory inbreeding allele values became increasingly more frequent ($M_{a}<0$), causing inbreeding avoidance in mate choice. However, $M_{a}$ values were not as negative after $40000$ generations when post-copulatory inbreeding avoidance and polyandry were fixed as they were when no post-copulatory inbreeding avoidance occurred (e.g., compare Figure 4A with Figure 1A, and Figure 4B with Figure 2A). When post-copulatory inbreeding strategy was initialised for random fertilisation, existence of an already adaptive strategy of pre-copulatory inbreeding avoidance precluded evolution of polyandry and post-copulatory inbreeding avoidance (Figure 4C,D). Mean allele values affecting polyandry consistently decreased over generations regardless of the cost of post-copulatory inbreeding strategy, $c_{F}$. Consequently, when $c_{F}=0$, post-copulatory inbreeding strategy allele values had no effect because females were consistently monandrous, resulting in high drift of $F_{a}$ values among replicates (Figure 4C). However, when $c_{F}=0.02$, $F_{a}$ values remained near zero to minimise direct costs. This lack of evolution of post-copulatory inbreeding avoidance was driven by a lack of polyandry, and therefore an inability of females to bias fertilisation among multiple mates. When pre-copulatory inbreeding avoidance and polyandry were both fixed ($F_{a}=-10$ and $P_{a}=1$), post-copulatory inbreeding strategy evolved to similarly negative mean allele values as pre-copulatory inbreeding strategy did in Figure 4A,B (see Supporting Information).
